Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection

### 2016-09-28 paper/lncsFormat0929_LTDetector.tex
LTDetector version

\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
%构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
\maketitle

\begin{abstract}
Many web applications need the accurate event detection technique on microblog stream. 
But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
We develop a novel lightweight transfer learning method \textsc{LTDetector} to deal with the task.  
\textsc{LTDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and to make the transfer efficiently and effectively, the scale of knowledge should shrink without degrading. 
The following contributions are made in \textsc{LTDetector}.
%我们的核心贡献应该是说，我们提出了一个方法（结构Guided的词表抽取方法），用这个方法可以从维基中学习出来了一个高度准确的词表，这个词表对于迁移学习非常有效。
(1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level by utilizing the structure.
%结构提取的方法(without degrading)
Specifically, category's highly related words and their chi-square scores, namely category's \textit{KB State}, are condensed.
%The knowledge base's hierarchical structure is formalized as three-part: taxonomy graph, category-page bipartite graph, and page-content map.
%The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}, shrinking the scale of knowledge to category-word level.
(2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our proposed KB-Prior-LDA, which exploits the word co-occurrences and transfers the condensed knowledge \textit{KB State} into microblogs. 
%基于结构提取方法的迁移学习，学习到microblog的状态
(3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noise accurately. 
(4) Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed transfer learning method.
\textsc{LTDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
%另外，我们还标注了事件，使其语义可理解。以及LTDetector是efficient的。

@@

After Gibbs sampling on discrete time windows, \textsc{HS-Prior-LDA} learned all hidden topics of words.
And for a specific word type \(w\) and its history-state-like topic assignment \(c\) in time window \(t\), its document frequency is counted as \(n(c,t,w^{(c)})\), which is the element of category \(c\)'s \(t\)-th recent state.
Event detection on recent states is discussed in the following subsection.

\subsection{Detecting Events from Recent States}
\label{subsec:detection}
Text stream evolves more quickly with time than knowledge base.
For example, recent state of Military contain .
In other words, recent state is history-state-like topic timestamp.%在时间轴上的横截面。

The remaining time series analysis and text stream mining includes three phases: (1) bursty words; (2)phase; (3)tweet.
%An accurate recent states learning leads to accurate event detection.
\begin{rmk}[The Set of Events' Candidate Words] 
The set of events' candidate words \(\mathcal{B}_{c,t}\) are defined by the bursty words in recent state \(\bm{r}_{c,t}\).
\end{rmk}

\begin{rmk}[Event Phrase] 
Event phase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occurred in the set of events' candidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happened in time \(t\) under the category \(c\).
\end{rmk}

@@

@@

\textbf{Discussions.} 
These methods work in four ways. 
1) Based on topic model, BurstyBTM and TimeUserLDA detect bursty topics. 
Although they are designed for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
2) Integrated with knowledge base, Twevent detects bursty segments, groups them into clusters, and then filters out the meaningless ones by Wikipedia.
3) By clustering articles, UMass System and LSH decide whether the article belongs to the existing event or a new one.
As designed for First Story Detection task (one of the Topic Detection and Tracking subtasks\cite{allan2012topic}) initially, they prefer to enlarge the recall of detected events. 
4) By analyzing word frequencies, EDCoW clusters the bursty words into events.

>>>>

\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%\title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
%Category Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection
%构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
\maketitle

\begin{abstract}
Many web applications need the accurate event detection technique on microblog stream. 
But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
We develop a novel lightweight transfer learning method \textsc{LTDetector} to deal with the task.  
\textsc{LTDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and to make the transfer efficiently and effectively, the scale of knowledge should shrink without degrading. 
The following contributions are made in \textsc{LTDetector}.
%我们的核心贡献应该是说，我们提出了一个方法（结构Guided的词表抽取方法），用这个方法可以从维基中学习出来了一个高度准确的词表，这个词表对于迁移学习非常有效。
%Intrinsic
(1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level by utilizing the structure.
%结构提取的方法(without degrading)
Specifically, category's highly related words and their chi-square scores, namely category's \textit{KB State}, are condensed.
%The knowledge base's hierarchical structure is formalized as three-part: taxonomy graph, category-page bipartite graph, and page-content map.
%The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}, shrinking the scale of knowledge to category-word level.
(2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our KB-Prior-LDA, which exploits the word co-occurrences and transfers the knowledge base's category topics into microblogs. 
%基于结构提取方法的迁移学习，学习到microblog的状态
(3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noise accurately. 
(4) Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed transfer learning method.
\textsc{LTDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
%另外，我们还标注了事件，使其语义可理解。以及LTDetector是efficient的。

@@

After Gibbs sampling on discrete time windows, \textsc{HS-Prior-LDA} learned all hidden topics of words in microblog stream.
And for a specific word type \(w\) and its history-state-like topic assignment \(c\) in time window \(t\), its document frequency is counted as \(n(c,t,w^{(c)})\), which is the element of category \(c\)'s \(t\)-th recent state.
Event detection on recent states is discussed in the following subsection.

\subsection{Detecting Events from Recent States}
\label{subsec:detection}
Given the words' accurate meaning, events are  detected accurately as the patterns of words' time series are better exposed.
Taking the word \textit{hood} as an example, it belongs to the category \textit{Military} when it appeared in \textit{Ft Hood}, a US military establishment located in Texas.
As shown in Figure \ref{fig:hood}, the bursty pattern of \textit{hood} is clearly exposed after distinguishing its \textit{Military} time series from the raw time series.
%Therefore, the processing on each category's accurate stream states leads to the accurate event detection.

We take the detection in three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) linking event tweets with event phrases.
%这里添加对这几个Definition的解释。

\begin{rmk}[The Set of Events' Candidate Words] 
The set of events' candidate words \(\mathcal{B}_{c,t}\) are defined by the bursty words in recent state \(\bm{r}_{c,t}\).
\end{rmk}

\begin{rmk}[Event Phrase] 
Event phrase \(\mathcal{C}_{c,t,i}\) is the \(i\)-th combination of words which occurred in the set of events' candidate words \(\mathcal{B}_{c,t}\), and represents the \(i\)-th event happened in time \(t\) under the category \(c\).
\end{rmk}

@@

For a specific word \(w\) and the category \(c\), as stream states have provided the time series \(\{n(c,t_{1},w^{(c)}), \cdots, n(c,t_{T},w^{(c)})\}\), many bursty detection methods on the time series can be applied to check if the word \(w\) is bursty in category \(c\).  
%Text stream evolves more quickly with time than knowledge base.
%For example, recent state of Military contain .
%In other words, recent state is history-state-like topic timestamp.%在时间轴上的横截面。

@@

\textbf{Discussions.} 
%An accurate recent states learning leads to accurate event detection.
These methods work in four ways. 
1) Based on topic model, BurstyBTM and TimeUserLDA detect bursty topics. 
Although they are designed for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
2) Integrated with knowledge base, Twevent detects bursty segments, groups them into clusters, and then filters out the meaningless ones by Wikipedia.
3) By clustering articles, UMass System and LSH decide whether the article belongs to the existing event or a new one.
As designed for First Story Detection task (one of the Topic Detection and Tracking subtasks\cite{allan2012topic}) initially, they prefer to enlarge the recall of detected events. 
4) By analyzing word frequencies, EDCoW clusters the bursty words into events.
